Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-07 ms.tex
comments...
Adjusting table

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{lc}
\hline
{Variable} & {Definition} \\
\hline
$M_{\bullet}$ & Black hole mass \\
$\tilde{v}_{w}$ & Total heating parameter, including minimum heating rate from stellar velocity dispersion \\
$v_{w}$ & Total heating parameter, excluding heating rate from stellar velocity dispersion \\
$r_{s}$ & Stagnation radius (where radial velocity goes to zero) \\
$r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
$r_{\rm b}$ & outer break radius of stellar density profile \\ 
$r_{\rm Ia}$ & radius exterior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
$\rho_{\star}(r)$ & 3D radial stellar density profile \\
$\rho(r)$ & gas density of CNM \\
$M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
$M_{\rm enc}(r)$ & total encolsed mass inside radius $r$ (SMBH + stars) \\
$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
$\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
$\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
$\Gamma$ & power-law slope of radial stellar density profile interior to the break radius \\
$\sigma(r)$ & stellar velocity dispersion \\
$\dot{M}$ & mass accretion rate \\
$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]) \\
$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
$\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
$t_{\rm h}$ & Hubble timescale \\
\hline
\label{table:definitions}  
\end{tabular}
\begin{tablenotes}
\item{$^{(a)}FILL IN$}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccc}
  \hline
  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$}  \\
  ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
\hline
 & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
  $    10^{ 6 }$ & 300 & 100 & & $ 1.3 \times 10^{ -5 }$ & $ 1.1 \times 10^{ 2 }$ \\
  ... & 600  & 100 & &$ 2.2 \times 10^{ -6 }$ & $ 8.1 \times 10^{ 3 }$ \\
   ...    & 1200  & 100 & &$ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ \\
  $    10^{ 7 }$ & 300 & 100 & & $ 1.0 \times 10^{ -4 }$ & 6.5 \\
 ...    & ...   & 25 & &$ 7.8 \times 10^{ -5 }$ & 17 \\
 ...      & ...   & 50 & &$ 7.9 \times 10^{ -5 }$ & 12 \\
   ...    & ...   & 200 & &$ 1.2 \times 10^{ -4 }$ & $\mathbf{4.7}$ \\
   ...    & ...   & 400 & &$ 3.6 \times 10^{ -4 }$ & $\mathbf{1.2}$ \\
   ...     & 600  & 100 && $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ \\
   ...     & 1200  & 100 && $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ \\
  $    10^{ 8 }$ & 300 & 100 & & $ 6.6 \times 10^{ -4 }$ & $\mathbf{1.4}$ \\
...     & ...  & 25 & &$ 1.9 \times 10^{ -4 }$ & 12 \\
   ...     & ...  & 50 & &$ 3.3 \times 10^{ -4 }$ &
  $\mathbf{4.6}$ \\
     ...$^{\dagger}$ & ...  & 50& & $ 9.1 \times 10^{ -4 }$ &
  $\mathbf{5.6}$ \\
   ... & ... & 200 && $ 1.4 \times 10^{ -3 }$ &
  $\mathbf{0.43}$ \\
   ...     & 600  & 100 && $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ \\
   ...     & 1200  & 100 && $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ \\
  \hline
 & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
$    10^{ 6 }$ & 600  &25 & & $ 1.6 \times 10^{ -6 }$ & $ 1.6 \times 10^{ 3 }$ \\
  ...  & 600  & 50 & &$ 1.7 \times 10^{ -5 }$ & $\mathbf{33}$ \\
  ...  & 1200  & 100 && $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ \\
  $    10^{ 7 }$ & 1200  & 100& & $ 5.1 \times 10^{ -7 }$ & $ 9.4 \times 10^{ 4 }$ \\
  ...  & 600  & 50 && $ 4.5 \times 10^{ -5 }$ & $\mathbf{21}$ \\
  ...  & ...  & 25 & &$ 8.5 \times 10^{ -6 }$ & $ 4.6 \times 10^{ 2 }$ \\
$10^{8}$  & 300  & 50 & & $ 6.0 \times 10^{ -5 }$ & 56 \\
  ...  & 600  & 100 & &$ 8.0 \times 10^{ -4 }$ & $\mathbf{1.6}$ \\
  ...  &  ...  & 25 && $ 2.3 \times 10^{ -5 }$ & $ 2.8 \times 10^{ 2 }$ \\
  ...  &  ...  & 50 && $ 6.0 \times 10^{ -5 }$ & 56 \\
... & 1200 & 100 && $ 2.4 \times 10^{ -6 }$ & $ 2.1 \times 10^{ 4 }$ \\
  ...  & ...  & 50 && $ 2.0 \times 10^{ -6 }$ & $ 3.1 \times 10^{ 4 }$ \\
  ...  &  ...  & 200 && $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ \\
  ...  &  ... & 400 && $ 1.2 \times 10^{ -3 }$ & $\mathbf{4.6}$ \\
  \hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold
text.  $\dagger$Calculated with full radiative cooling included, assuming mass loss parameter $\eta = $? 
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
source (stars, MSPs, SNe Ia, and black hole feedback) calculated for
the average star formation history of galaxies containing a given
black hole mass.  Again, Ia heating is suppressed in low mass galaxies
because the Ia radius exceeds the nominal stagnation radius (bottom
panel).  MSP heating is again found to be negligible for all black
hole masses.  The younger stellar populations characterizing galaxies
with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind
and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and
$v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most
massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack
of young stellar populations significantly reduce the role of stellar
wind
heating.  %Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
Strikingly, {\it we find that galactic nuclei experiencing the same
  average star formation history as their host galaxies produce
  thermally stable flows across all black hole masses}.  {\bf NCS:
  deleted a sentence referring to old results on thermal instability -
  it is now correct to say we are thermally stable everywhere, yes? AG
 though note our kludgy way of including Ias if rs is inside of rIa.}

@@

{\bf NCS: is this reduced heating rate thermally unstable under Aleksey's revised formula?  We should comment}

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Definitions of commonly used variables}
\begin{tabular}{ll}
\hline
{Variable} & {Definition} \\
\hline
$M_{\bullet}$ & Black hole mass \\
$\tilde{v}_{w}$ & Total heating parameter, including minimum heating rate from stellar velocity dispersion \\
$v_{w}$ & Total heating parameter, excluding heating rate from stellar velocity dispersion \\
$r_{s}$ & Stagnation radius (where radial velocity goes to zero) \\
$r_{\rm soi}$ & radius of sphere of influence (eq.~[\ref{eq:rsoi}]) \\
$r_{\rm b}$ & outer break radius of stellar density profile \\ 
$r_{\rm Ia}$ & radius exterior to which Ia SN are infrequent compared to the dynamical/inflow timescale (eq.~[\ref{eq:rIa}]) \\ 
$\rho_{\star}(r)$ & 3D radial stellar density profile \\
$\rho(r)$ & gas density of CNM \\
$M_{\star}(r)$ & total enclosed stellar mass inside radius $r$ \\
$M_{\rm enc}(r)$ & total encolsed mass inside radius $r$ (SMBH + stars) \\
$q(r)$ & mass source term due to stellar winds (eq.~[\ref{eq:q}]) \\
$\eta$ & parameter setting normalization of mass input from stellar winds (eq.~[\ref{eq:q}]) \\
$\tau_{\star}$ & age of stellar population, in case of a single burst of star formation \\
$\Gamma$ & power-law slope of radial stellar density profile interior to the break radius \\
$\sigma(r)$ & stellar velocity dispersion \\
$\dot{M}$ & mass accretion rate \\
$\dot{M}_{\rm Ia}$ & maximum mass accretion rate as limited by SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]) \\
$\dot{M}_{\rm C}$ & equilibrium accretion rate set by Compton heating (eq.~[\ref{eq:MdotC}]) \\
$\dot{M}_{\rm TI}$ & maximum accretion rate for thermally stable accretion (eq.~[\ref{eq:Mdotmax}]) \\
$\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|$ & ratio of external heating (stellar winds, SN Ia, MSPs) to radiative cooling (eq.~[\ref{eq:cooling2}]) \\
$t_{\rm h}$ & Hubble timescale \\
\hline
\label{table:definitions}  
\end{tabular}
\begin{tablenotes}
\item{$^{(a)}FILL IN$}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccc}
  \hline
  {$M_{\bullet}$} & {$v_{w}$} & {$r_b^{(b)}$} &  $r_{\rm s}/r_{\rm soi}$ &  {$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.2}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.2}{\eta}\right)_{r_s}^{(d)}$}  \\
  ($M_{\odot}$) & (km s$^{-1}$) & (pc) &- & - & - &  & \\ 
\hline
 & & & Cusp Galaxies, $\Gamma^{(a)} = 0.8$ & & & & & \\
 $    10^{ 6 }$ & 300 & 0.8 & 100 & $ 6.4 \times 10^{ -5 }$ & 17 \\
... & 600 & 0.8 & 100 & $ 1.1 \times 10^{ -5 }$ & $ 1.6 \times 10^{ 3 }$ \\
... & 1200 & 0.8 & 100 & $ 1.9 \times 10^{ -6 }$ & $ 7.2 \times 10^{ 4 }$ \\
$    10^{ 7 }$ & 300 & 0.8 & 25 & $ 3.9 \times 10^{ -4 }$ & 1.8 \\
... & ... & 0.8 & 50 & $ 3.9 \times 10^{ -4 }$ & $\mathbf{0.82}$ \\
... & ... & 0.8 & 100 & $ 5.2 \times 10^{ -4 }$ & $\mathbf{0.33}$ \\
... & ... & 0.8 & 200 & $ 5.9 \times 10^{ -4 }$ & $\mathbf{0.18}$ \\
... & ... & 0.8 & 400 & $ 1.8 \times 10^{ -3 }$ & $\mathbf{ 1.9 \times 10^{ -2 }}$ \\
... & 600 & 0.8 & 25 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & ... & 0.8 & 100 & $ 3.6 \times 10^{ -5 }$ & $ 4.4 \times 10^{ 2 }$ \\
... & 1200 & 0.8 & 100 & $ 6.4 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 4 }$ \\
$    10^{ 8 }$ & 300 & 0.8 & 25 & $ 9.4 \times 10^{ -4 }$ & $\mathbf{1}$ \\
... & ... & 0.8 & 50 & $ 1.6 \times 10^{ -3 }$ & $\mathbf{0.19}$ \\
... & ... & 0.8 & 100 & $ 3.3 \times 10^{ -3 }$ & $\mathbf{ 2.2 \times 10^{ -2 }}$ \\
... & ... & 0.8 & 200 & $ 7.2 \times 10^{ -3 }$ & $\mathbf{ 2.1 \times
  10^{ -3 }}$ \\
$    10^{ 8 }$ & 450 & 0.8 & 100 & $ 4.4 \times 10^{ -4 }$ & 4 \\
...$^{\dagger}$ & ... & 0.8 & 100 & $ 2.8 \times 10^{ -3 }$ & $\mathbf{2.8}$ \\
... & 600 & 0.8 & 25 & $ 1.3 \times 10^{ -4 }$ & $ 1.1 \times 10^{ 2
}$ \\
... & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 76 \\
...$^{\dagger}$ & ... & 0.8 & 100 & $ 1.5 \times 10^{ -4 }$ & 70 \\
... & ... & 0.8 & 200 & $ 1.5 \times 10^{ -4 }$ & 67 \\
... & ... & 0.8 & 400 & $ 1.6 \times 10^{ -4 }$ & 58 \\
... & 1200 & 0.8 & 100 & $ 2.0 \times 10^{ -5 }$ & $ 7.2 \times 10^{ 3 }$ \\
  \hline
 & & & Core Galaxies, $\Gamma = 0.1$ & & & & & & \\
$    10^{ 6 }$ & 600 & 0.1 & 25 & $ 8.2 \times 10^{ -6 }$ & 99 \\
... & ... & 0.1 & 50 & $ 8.5 \times 10^{ -5 }$ & $\mathbf{0.45}$ \\
... & 1200 & 0.1 & 25 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 50 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
... & ... & 0.1 & 100 & $ 2.9 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ \\
$    10^{ 7 }$ & 600 & 0.1 & 25 & $ 4.3 \times 10^{ -5 }$ & 41 \\
... & ... & 0.1 & 50 & $ 2.3 \times 10^{ -4 }$ & $\mathbf{0.38}$ \\
... & 1200 & 0.1 & 25 & $ 1.8 \times 10^{ -6 }$ & $ 2.2 \times 10^{ 4 }$ \\
... & ... & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 1.7 \times 10^{ 4 }$ \\
... & ... & 0.1 & 100 & $ 2.5 \times 10^{ -6 }$ & $ 9.8 \times 10^{ 3 }$ \\
$    10^{ 8 }$ & 600 & 0.1 & 25 & $ 1.1 \times 10^{ -4 }$ & 31 \\
... & ... & 0.1 & 50 & $ 3.0 \times 10^{ -4 }$ & 3 \\
... & ... & 0.1 & 100 & $ 4.0 \times 10^{ -3 }$ & $\mathbf{ 5.7 \times 10^{ -3 }}$ \\
... & 1200 & 0.1 & 25 & $ 8.4 \times 10^{ -6 }$ & $ 5.6 \times 10^{ 3 }$ \\
... & ... & 0.1 & 50 & $ 9.8 \times 10^{ -6 }$ & $ 4.0 \times 10^{ 3 }$ \\
... & ... & 0.1 & 100 & $ 1.2 \times 10^{ -5 }$ & $ 2.4 \times 10^{ 3 }$ \\
... & ... & 0.1 & 200 & $ 2.1 \times 10^{ -5 }$ & $ 6.5 \times 10^{ 2 }$ \\
... & ... & 0.1 & 400 & $ 6.2 \times 10^{ -3 }$ & $\mathbf{ 5.8 \times 10^{ -3 }}$ \\
  \hline

\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.2$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold
text.  $\dagger$Calculated with full radiative cooling included, assuming mass loss parameter $\eta = $? 
\end{tablenotes}
\end{minipage}
\end{threeparttable}

@@

Figure~\ref{fig:vwSources} shows $\vwO(M_{\bullet})$ from each heating
source (stars, MSPs, SNe Ia, and black hole feedback) calculated for
the average star formation history of galaxies containing a given
black hole mass.  Again, Ia heating is suppressed in low mass galaxies
because the Ia radius exceeds the nominal stagnation radius (bottom
panel).  MSP heating is again found to be negligible for all black
hole masses.  The younger stellar populations characterizing galaxies
with $\Mbh\lsim 5\times 10^{8} \Msun$ are dominated by stellar wind
and Ia heating, with $v_{w}^{\star} \sim 1000$ km s$^{-1}$ and
$v_w^{\rm Ia} \sim 500$ km s$^{-1}$, respectively.  Only for the most
massive galaxies, with $\Mbh\gsim 5\times 10^{8} \Msun$, does the lack
of young stellar populations significantly reduce the role of stellar
wind
heating.  %Solid and dashed lines again show black hole masses for which the flow is thermally stable and thermally unstable, respectively, with $(\dot{q}_{\rm heat}/|\dot{q}_{\rm rad}|)_{r_{s}}$ as a function of $M_{\bullet}$ shown in the bottom panel.
Strikingly, {\it we find that galactic nuclei experiencing the same
  average star formation history as their host galaxies produce
  thermally stable flows across all black hole masses}.  {\bf NCS:
  deleted a sentence referring to old results on thermal instability -
  it is now correct to say we are thermally stable everywhere, yes? AG
  though note our kludgy way of including Ias if rs is inside of
  rIa. I also don't think it is fair to say that we obtain stability
  for large Mbh as the heating parameter would become comparable to
  the velocity dispersion.}

@@

{\bf NCS: is this reduced heating rate thermally unstable under
  Aleksey's revised formula?  We should comment. AG: What revised
  formula.}
